% Created 2024-07-31 Wed 22:13
% Intended LaTeX compiler: pdflatex
\documentclass{resume}

% Change the page layout if you need to
\usepackage[utf8]{inputenc}
\usepackage[left=0.95in,top=0.95in,right=0.95in,bottom=0.95in]{geometry} % Document margins
\usepackage[colorlinks=true,allcolors=cyan]{hyperref}
\usepackage{breakurl}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Adithya Bhat} % Your name
\address{
    \\ Email - \href{mailto:aditbhat@visa.com}{aditbhat@visa.com} \\
    GitHub - \href{https://github.com/adithyabhatkajake}{https://github.com/adithyabhatkajake}
}
\address{
    \\ Website - \href{https://adithyabhatkajake.github.io}{https://adithyabhatkajake.github.io}
}
\address{Visa Research, Visa Inc., CA} % Your address
\author{Adithya Bhat}
\date{}
\title{Curriculum Vitae}
\hypersetup{
 pdfauthor={Adithya Bhat},
 pdftitle={Curriculum Vitae},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.3 (Org mode 9.6.15)}, 
 pdflang={English}}
\begin{document}


\begin{rSection}{Research Interests}
\label{sec:orgdea95f7}
My interests are \emph{Byzantine fault-tolerant distributed systems}, \emph{applied cryptography} and \emph{blockchain protocols}.
My work aims at developing and evaluating cryptographic solutions for secure, fault-tolerant distributed systems.
My current research focuses on energy-efficient consensus protocols in network settings such as synchronous, asynchronous, and all intermediate models; fault-tolerant cryptographic protocols such as PVSS and Random Beacons, and secure Byzantine fault-tolerant distributed protocols.
\end{rSection}
\begin{rSection}{Education}
\label{sec:org5f8902f}
 \item  \textbf{Purdue University, West Lafayette}
 \hfill  \emph{(2018-2023)}\\[0pt]
    Advisor: Aniket Kate\\[0pt]
    Ph.D., Department of Computer Science

 \item  \textbf{National Institute of Technology Karnataka, Surathkal}
 \hfill  \emph{(2014-2018)}\\[0pt]
    Bachelor of Technology, Information Technology
\end{rSection}
\begin{rSection}{Work Experience}
\label{sec:orgc679fe4}
\textbf{Visa Research, Foster City}  \hfill  (Aug 2023 - Present)\\[0pt]
\emph{Staff Research Scientist}  \hfill  \emph{(Anderson Nascimento)}


\textbf{Visa Research, Palo Alto}  \hfill  (May 2022 - Aug 2022)\\[0pt]
\emph{Ph.D. Research Intern}  \hfill  \emph{(Mahdi Zamani)}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
 \item   Developed \emph{FastSync}: an efficient blockchain synchronization protocol 
 \item   Developed an efficient partially synchronous sharding protocol and implemented Instachain
\end{list}
\vspace{0.5em} % Some space after the list of bullet points

\textbf{VMware Research, Remote}  \hfill  (May 2021 - Aug 2021)\\[0pt]
\emph{Research Intern}  \hfill  \emph{(Alin Tomescu, Ittai Abraham)}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
 \item   Built a prototype of anonymous token system using Concord-BFT 
 \item   Developed \emph{quick-pay}: a one-round trip low-latency payment system 
 \item   Developed a two-phase lock-free sharding solution using quick-pay
\end{list}
\vspace{0.5em} % Some space after the list of bullet points

\textbf{Purdue University, West Lafayette}  \hfill  (Aug 2018 - Aug 2023)\\[0pt]
\emph{Graduate Research Assistant}  \hfill  \emph{(Aniket Kate)}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
 \item   Researching energy efficient Byzantine fault tolerant consensus protocols. 
 \item   Developed mathematical models for protocol optimization to improve energy efficiency. 
 \item   Implemented, evaluated, and simulated cryptographic and distributed system protocols.
\end{list}
\vspace{0.5em} % Some space after the list of bullet points

\textbf{Indian Statistical Institute, Kolkata}  \hfill  (July 2017 - December 2017)\\[0pt]
\emph{Undergraduate Research Fellow}  \hfill  \emph{(Sushmitha Ruj)}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
 \item   Designed a storage auditing library based on compact proofs of retrievability. 
 \item   Implemented new transactions on an Ethereum client to build a publicly verifiable data-storage system.
\end{list}
\vspace{0.5em} % Some space after the list of bullet points

\textbf{Morgan Stanley, Bangalore}  \hfill  (May 2017 - July 2017)\\[0pt]
\emph{Software Analyst}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
 \item   Worked on evaluating an elastic-search visualization plugin for the LevelDB database.
\end{list}
\vspace{0.5em} % Some space after the list of bullet points

\textbf{Indian Institute of Science, Bangalore}  \hfill  (May 2016 - July 2016)\\[0pt]
\emph{Indian Academy of Sciences Summer Research Fellow}  \hfill  \emph{(C. E. Veni Madhavan)}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
 \item   Evaluated Pollard's rho, William's \(p+1\), \(p-1\) factorization, and elliptic curve factorization methods for efficient batch factorization of numbers generated during the sieving phase of GGNFS.
\end{list}
\vspace{0.5em} % Some space after the list of bullet points
\end{rSection}

\begin{rSection}{Publications}
\label{sec:org0ffd259}
\vspace{0.5em}
\begin{enumerate}
\item \label{orgc2aa619} \emph{SensorBFT: Fault-Tolerant Target Localization using Voronoi Diagrams and Approximate Agreement.} \textbf{ICDCS 2024}. Akhil Bandarupalli, Adithya Bhat, Somali Chaterji, Michael K. Reiter, Aniket Kate, Saurabh Bagchi.
\item \label{orge4db138} \emph{Delphi: Efficient Asynchronous Approximate Agreement for Distributed Oracles.} \textbf{DSN 2024}. Akhil Bandarupalli, Adithya Bhat, Saurabh Bagchi, Aniket Kate, Chen-Da Liu-Zhang, and Michael K. Reiter. \href{https://arxiv.org/pdf/2405.02431}{eprint}
\item \label{org25ac787} \emph{HashRand: Efficient Asynchronous Random Beacon without Threshold Cryptographic Setup.} \textbf{CCS 2024}. Akhil Bandarupalli, Adithya Bhat, Saurabh Bagchi, Aniket Kate, and Michael Reiter. \href{https://eprint.iacr.org/2023/1755.pdf}{eprint}
\item \label{org9bf3f63} \emph{Attacking and Improving the Tor Directory Protocol.} \textbf{IEEE S\&P 2024}. Zhongtang Luo, Adithya Bhat, Kartik Nayak, and Aniket Kate. \href{https://zhtluo.com/paper/Attacking\_and\_Improving\_the\_Tor\_Directory\_Protocol.pdf}{eprint}
\item \label{org473d87d} \emph{EESMR - Energy Efficient State Machine Replication.} \textbf{Middleware 2023}. Adithya Bhat, Akhil Bandarupalli, Manish Nagaraj, Saurabh Bagchi, Aniket Kate, Michael Reiter. \href{https://dl.acm.org/doi/10.1145/3590140.3592848}{conference} \href{https://arxiv.org/abs/2304.04998}{eprint}
\item \label{org5a1964c}\label{org3c2d425} \emph{The unique chain rule and its applications.} \textbf{Financial Cryptography 2023}. Adithya Bhat, Akhil Bandarupalli, Saurabh Bagchi, Aniket Kate, Michael Reiter. \href{https://fc23.ifca.ai/preproceedings/138.pdf}{pre-conference} \href{https://doi.org/10.1007/978-3-031-47754-6\_3}{conference} \href{https://eprint.iacr.org/2021/180}{eprint} \href{https://github.com/adithyabhatkajake/libchatter-rs}{code}
\item \label{org1ff6573} \emph{OptRand - Optimistically Responsive Reconfigurable Distributed Randomness.} \textbf{NDSS 2023}. Adithya Bhat, Nibesh Shrestha, Aniket Kate, Kartik Nayak. \href{https://www.ndss-symposium.org/ndss-paper/optrand-optimistically-responsive-reconfigurable-distributed-randomness/}{conference} \href{https://eprint.iacr.org/2022/193}{eprint} \href{https://github.com/nibeshrestha/optrand}{protocol code} \href{https://github.com/libdist-rs/optrand-rs}{crypto code} \href{https://www.youtube.com/watch?v=6DH2bGXP3-4}{video}
\item \emph{OpenSquare: Decentralized Repeated Modular Squaring Service.} \textbf{CCS 2021}. Sri Aravinda Krishnan Thyagarajan, Tiantian Gong, Adithya Bhat, Aniket Kate, Dominique Schroder. \href{https://dl.acm.org/doi/10.1145/3460120.3484809}{conference} \href{https://eprint.iacr.org/2021/1273}{eprint} \href{https://github.com/verifiable-timed-signatures/OpenSquare}{code}
\item \label{org40d7006} \emph{RandPiper – Reconfiguration Friendly Random Beacons with Quadratic Communication.} \textbf{CCS 2021}. Adithya Bhat, Nibesh Shrestha, Aniket Kate, Kartik Nayak. \href{https://dl.acm.org/doi/abs/10.1145/3460120.3484574}{conference} \href{https://eprint.iacr.org/2020/1590.pdf}{eprint} \href{https://github.com/zhtluo/randpiper-rs}{code}
\item \label{org7de989c} \emph{Reparo - Publicly Verifiable Repair Layer for any Blockchain.} \textbf{FC 2021}. Sri Aravinda Krishnan Thyagarajan, Adithya Bhat, Bernardo Magri, Daniel Tschudi, Aniket Kate. \href{https://fc21.ifca.ai/papers/119.pdf}{conference} \href{https://arxiv.org/abs/2001.00486}{eprint}
\item \label{orgb3047d8} \emph{Verifiable Timed Signatures for Blockchains.} \textbf{CCS 2020}. Sri Aravinda Krishnan Thyagarajan, Adithya Bhat, Guilio Malavolta, Nico Dottling, Aniket Kate, Dominique Schroder. \href{https://dl.acm.org/doi/10.1145/3372297.3417263}{conference} \href{https://eprint.iacr.org/2020/1563.pdf}{eprint} \href{https://github.com/verifiable-timed-signatures/liblhtlp}{code}
\end{enumerate}
\end{rSection}
\begin{rSection}{Tech Reports}
\label{sec:org44c4a44}
\begin{enumerate}
\item \label{org5025cfb} \emph{Synchronous Distributed Key Generation without Broadcasts.} Nibesh Shrestha, \textbf{Adithya Bhat}, Kartik Nayak, Aniket Kate. \href{https://eprint.iacr.org/2021/1635}{eprint}
\item \label{orgd23fc1b} \emph{Leto - Partially Synchronous Unique Chains made flexible.} \textbf{Adithya Bhat}, Saurabh Bagchi, Aniket Kate, Michael Reiter. \href{https://github.com/libdist-rs/leto-rs}{code}
\item \label{orgc62de0e} \emph{Using the future to verify the past.} Adithya Bhat, Mohsen Minaei, Mahdi Zamani. Appeared in CESC, 2022. \textbf{U.S. Patent pending.}
\item \label{orgc471416} \emph{UTT: Decentralized Ecash with Accountable Privacy.} \textbf{Science of Blockchain Conference 2023}. Alin Tomescu, Adithya Bhat, Benny Applebaum, Ittai Abraham, Guy Gueta, Benny Pinkas, and Avishay Yanai. \href{https://eprint.iacr.org/2022/452}{eprint} \href{https://github.com/definitelyNotFBI/utt}{code}
\end{enumerate}
\end{rSection}
\begin{rSection}{Software Artifacts}
\label{sec:org8a13abb}
\begin{enumerate}
\item Developed a synchronous networking library to implement SMR protocols. \href{https://github.cowwm/adithyabhatkajake/libchatter-rs}{code}  \hfill  (Rust)
\item Implemented Apollo [\ref{org5a1964c}] (protocol node, normal client and special client) using the Rust networking library. \href{https://github.com/adithyabhatkajake/libchatter-rs}{code}  \hfill  (Rust)
\item Implemented Sync HotStuff (normal protocol node, round robin protocol node, client) using the Rust networking library. \href{https://github.com/adithyabhatkajake/libchatter-rs}{code}  \hfill  (Rust)
\item Developed a plug-and-play framework using libp2p to run and simulate distributed system protocols. The framework provides interfaces to aid faster prototyping of distributed system protocols. \href{https://github.com/adithyabhatkajake/libchatter/}{code}  \hfill  (Go-lang)
\item Implemented Sync HotStuff using the go networking library. \href{https://github.com/adithyabhatkajake/libsynchs}{code}  \hfill  (Go-lang)
\item Implemented Apollo [\ref{org5a1964c}] using the go networking library. \href{https://github.com/adithyabhatkajake/libapollo}{code}  \hfill  (Go-lang)
\item Implementation of E2C [\ref{org473d87d}]. \href{https://github.com/adithyabhatkajake/libe2c-cpp}{code}  \hfill  (C++)
\item Developed a linearly homomorphic time-lock puzzle library. \href{https://github.com/verifiable-timed-signatures/liblhtlp}{code}  \hfill  (C)
\end{enumerate}
\end{rSection}
\begin{rSection}{Talks}
\label{sec:org082a94d}
\begin{enumerate}
\item Reconfiguration-friendly Byzantine Fault-tolerant Distributed randomness. \href{https://adithyabhatkajake.github.io/assets/presentations/KU-Leuven-RandomBeacons.pptx}{slides}  \hfill  \emph{(KU Leuven)}
\item Unique Chain Rule and its applications. \href{https://adithyabhatkajake.github.io/assets/presentations/Unique-Chain-Rule-Applications.pptx}{slides}  \hfill  \emph{(FC 2023)}
\item Reconfiguration-friendly Byzantine Fault-tolerant Distributed randomness. \href{https://adithyabhatkajake.github.io/assets/presentations/BU-RandomBeacons.pptx}{slides}  \hfill  \emph{(Boston University)}
\item Flexible State Machine Replication. \href{https://adithyabhatkajake.github.io/assets/presentations/Midwest-crypto-day-Lightning-Talk.pptx}{slides}  \hfill  \emph{(Midwest Crypto Day - Lightning session)}
\item OptRand - Optimistically Responsive Reconfigurable Distributed Randomness. \href{https://www.youtube.com/watch?v=6DH2bGXP3-4}{video}  \hfill  \emph{(NDSS 2023)}
\item FastSync: Using the future to verify the past. \href{https://www.youtube.com/watch?v=kCqrd1MQ1no\&t=3341s}{video} \hfill  \emph{(CESC 2022)}
\item RandPiper - Reconfiguration friendly random beacons with quadratic communication. \hfill  \emph{(CCS 2021)}
\item Reparo - Publicly Verifiable Repair Layer for any blockchain. \href{https://youtube.com/watch?v=jV\_Pjc17eWY}{video}  \hfill  \emph{(FC 2021)}
\item Transitive network - A tokenless IOU-based Credit Network. Cryptocurrency Implementers Workshop.  \hfill  \emph{(FC 2019)}
\end{enumerate}
\end{rSection}
\begin{rSection}{Academic Service}
\label{sec:org34c1689}
\begin{itemize}
\item Program Committee:
\begin{itemize}
\item CCS 2024
\end{itemize}
\end{itemize}
\begin{itemize}
\item Reviewer for
\begin{itemize}
\item 2024: ACM TOPS, Journal of Cryptology
\item 2023: SOSP AEC, IET
\end{itemize}
\item External Reviewer for
\begin{itemize}
\item 2024: IEEE S \& P
\item 2023: CCS, IET, Middleware, IEEE S \& P
\item 2022: CCS, PODC, IEEE S \& P, CESC
\item 2021: AFT, FC, PODC, IEEE S \& P
\item 2020: Usenix Security, IEEE S \& P
\item 2019: NDSS
\end{itemize}
\end{itemize}
\end{rSection}
\end{document}
